\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference for Deformation Monitoring}

### 2021-09-21 paper/r1/manuscript-mssp.tex
basic revision

		\title{GNSS-based \textcolor{r_s}{Short-term} Displacement Detection Using Bayesian Inference for Deformation Monitoring}

		%% use optional labels to link authors explicitly to addresses:
		%% \author[label1,label2]{}
		%% \address[label1]{}
		%% \address[label2]{}

		\author[a]{Nan Shen}
		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
		\cortext[mycorrespondingauthor]{Corresponding author}
		\ead{l.chen@whu.edu.cn}
		\author[a]{Ruizhi Chen}
		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
		\begin{abstract}
		Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics.
		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
%		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
%		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results in a short time.
		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
		Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
		%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
		By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
		Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
		Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.		
		\end{abstract}

@@

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	To evaluate the performance of single base station real time kinematic(RTK) and network real time kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	\textcolor{r_s}{
		Moschas et al.\cite{Moschas_2014} studied the extraction of strong motion displacement waveform by PPP and evaluated it through free vibration experiments. These results show that 10 Hz PPP-GPS is very useful for seismic engineering and can be safely used to reconstruct the deflection waveforms of various points on the ground and structure during strong motion.}
	\textcolor{r_s}{Zhang et al.\cite{Meng_2019} introduced Galileo augmenting GPS single-frequency single-epoch precise positioning method with baseline constrain for bridge dynamic monitoring, to improve the positioning availability and reliability, as well as narrow the search space, and increase the success rate of ambiguity resolution and positioning.
	Xue et al.\cite{Xue2021} comprehensively evaluated multi-GNSS low-cost receivers for deformation monitoring and concluded that the potential improvement of the precision of the low-cost receiver by using multi-GNSS measurements and a GNSS base station with a geodetic antenna.}
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	\textcolor{r_s}{
	The other category is about displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	\textcolor{r_s}{
		Betti et al.\cite{betti2001deformation,betti2011deformation} studied the use of the Bayesian approach to evaluating deformation from GPS time series, in which a test procedure was constructed under the Bayesian framework. However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test, and the control network processing results are generally based on repeated static adjustment.
	}

@@

	% 仿真实验中不同基于索引检测方法的指标值如图6所示。
	% 从中可以看出不同探测方法所采用的指标的数值范围不一致，但在所设计的突变处很明显。
	%  然而，想基于这些指标值自动将这些突变点识别出来，还需要额外的工作。
	%  另外，这些方法设计之初为了探测突变点，并未涉及位移提取。
	%  有学者，基于设计了基于这些指标的突变探测和位移提取方法，但实时过程复杂。
	%  相比而言，本文提出的方法是一种简单直接易于实现的一站式方法。
	The index values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
	It can be seen that the numerical range of indicators used by different detection methods is not consistent, but all are obvious at the designed abrupt point.
	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold.
	In addition, these methods were originally designed to detect abrupt points without involving displacement extraction.
	There are abrupt detection and displacement extraction methods based on these indicators, but the implementation process is complex\cite{shen_shortterm2021}.
	In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_sigma_sim_simple}
		\caption{Histogram of posterior sample of $\sigma$ in the simulation experiment.}
		\label{fig_v_sigma_sim_simple}
	\end{figure} 
	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{v_sim_idx}
	\caption{Index values of different index-based detection methods in simulation experiments.}
	\label{fig_v_sim_idx}
	\end{figure} 
	\subsection{Field Experiments}
	The experiments were carried out on the roof of a building on the campus of Wuhan University, and the equipment deployment is shown in Fig. \ref{fig_v_field_exp_config}. 
	A hard plank was pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank. 
	One receiver antenna was fixed on the plank as a rover, and the other receiver antenna was installed on a tripod beside it as the base station. 
	Both antennas were connected to BD992 OEM boards on the table, and the OEM boards were connected to the laptops for data collection. 
	As shown in subgraphs (c) and (d), the height of the antenna was measured with a tape before and after each movement of the object hanging on the plank. 
	Five readings were taken for each measurement to ensure data reliability.
	Besides, markers are made on the ground and on the antenna respectively to ensure that the same position was referenced for each measurement. 
	The sampling frequency of the GNSS receiver is set to 1 Hz. 
	We did two experiments, each lasting nearly 45 minutes. 
	During the experiment, the object hanging on the board was manually moved several times.
	The displacement amplitude of the second experiment is smaller than that of the first experiment.
	The GNSS observation data collected above are processed by the open-source software RTKLIB\cite{takasu2011rtklib}. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.5]{v_field_exp_config}
		\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
		\label{fig_v_field_exp_config}
	\end{figure}

@@

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
		\label{fig_v_ndop_snrmp_9_3}
	\end{figure} 
	The index values of different index-based detection methods in field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

	The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively. The two displacements measured by tape are -29.66 mm and -27.18 mm respectively. 
	To our surprise, the displacement difference between the two methods at the two change points is 1.58 mm and 11.46 mm, respectively. 
	The main reason is that the displacement control device is not fully controllable. 
	It can be seen from Fig. \ref{fig_v_bd9_3_up_ts} that before the second displacement change, the plank appears obvious floating when measuring with the tape. 
	As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
	%我们发现此处变点后验样本中的两个峰值对于均值和标准差中没有出现。
	%主要原因是变点的峰值距离很近，对于划分的段没有很明显的影响，因此对后验均值和标准差的浮动没有很大影响。
	%而在现实中，这种情况是会发生的，例如滑坡或者沉降，整个位移变化过程需要一定的时间，存在多个变化点。
	%然而，我们可能更加关注主要变化点，后面通过加入额外先验来提升主要变化点的识别，弱化次要变化点。

	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
		\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
		\label{fig_v_bd9_3_up_sigma}
	\end{figure} 
	Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
	In reality, multiple change points exist, such as multiple displacements in a short period of time in the process of landslide or settlement.
	However, more attention is paid to the primary change points.
	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
	\subsubsection{Field Experiment 2}%rover_bd9_4 part(650)
	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
	The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
	In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.

@@

	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{ndop_snrmp_9_4}
	\caption{Number of satellites, GDOP, SNR, multipath of experiment 2.}
	\label{fig_v_ndop_snrmp_9_4}
	\end{figure} 
	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
	The time series are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. The results are shown in Fig. \ref{fig_v_bd9_4_up_tau}, \ref{fig_v_bd9_4_up_mu}, and \ref{fig_v_bd9_4_up_sigma}.

@@

	The displacement detection based on Bayesian inference can meet different needs by adding a priori, and has sufficient flexibility.
	In addition, the Bayesian inference implementation based on MCMC sampling used in this paper provides posterior samples, which is more conducive to problem analysis.
	This study provides the first comprehensive assessment of the Bayesian inference model for displacement identification and extraction from GNSS kinematic positioning.

>>>>

		\title{\textcolor{r_s}{Displacement Detection from GNSS Kinematic Positioning Using Bayesian Inference for Deformation Monitoring}}

		%% use optional labels to link authors explicitly to addresses:
		%% \author[label1,label2]{}
		%% \address[label1]{}
		%% \address[label2]{}
		\author[a]{Nan Shen}
		\author[a]{Liang Chen\corref{mycorrespondingauthor}}
		\cortext[mycorrespondingauthor]{Corresponding author}
		\ead{l.chen@whu.edu.cn}
		\author[a]{Ruizhi Chen}
		\address[a]{State Key Laboratory of Information Engineering in Surveying, Mapping and Remote Sensing, Wuhan University, Wuhan 430000, PR China}
		\begin{abstract}
		Displacement is an important parameter in engineering analysis in structural mechanics and geomechanics.
		For decades, displacement detection based on the Global navigation satellite system (GNSS) has increasingly been important for a wide range of applications, from landslide monitoring, subsidence survey, to industrial measurement. 
%		Most of the GNSS-based displacement detection methods in these applications are based on GNSS long-term static positioning results.
%		With the development of the Internet of Things (IoT), high-precision GNSS positioning, and GNSS-related transmission protocol, kinematic positioning results can be transmitted to the cloud in real-time.
		However, due to the influence of measurement noise, it is still a challenge to identify and extract displacement from GNSS kinematic positioning results.
		To resolve this, we propose a novel displacement detection approach with the purpose of identifying and extracting displacement from GNSS kinematic positioning.
		Specifically, we use the Bayesian inference model to obtain the displacement change time from the coordinate time series of GNSS kinematic positioning. 
		%The likelihood function of the observation and the prior distribution of the parameters to be estimated are provided.
		%Finally, Bayesian inference was implemented by Markov Chain Monte Carlo (MCMC) sampling.
		By investigating the posterior distribution of the designed change point parameter, we can identify the change points.
		Furthermore, we derive the mean value from the posterior distribution of the mean parameter, and further obtain the displacement.
		Results from simulation and field experiments have demonstrated the effectiveness and flexibility of the proposed method.
		For significant displacement, it can be clearly identified; for small displacement, it can be identified by adding an interval constraint prior. The accuracy of up-displacement extraction from GNSS real-time kinematic positioning can reach within 2 mm in 15 minutes.		
		\end{abstract}

@@

	%位移探测算法回顾，
	%传统位移探测的弊端
	%位移探测的短板1,关注与定位算法，忽略探测算法2，关注与longterm忽略shortterm
	%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
	The first category is about the research of measurement technology in GNSS-based displacement detection.
	To evaluate the performance of single base station \textcolor{r_s}{real-time} kinematic(RTK) and network \textcolor{r_s}{real-time} kinematic(NRTK) in displacement detection, the data of different observation duration were compared\cite{wang2011gps}. The results showed that NRTK has advantages in accuracy and robustness.
	A displacement monitoring system was designed to evaluate NRTK for displacement detection\cite{GUMUS2019131}. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.
	In \cite{csanliouglu2016landslide} and \cite{lytvyn2012real}, the feasibility of displacement detection for landslides  using precise point position(PPP) has been studied. The results showed that PPP can be capable of detecting large landslides.
	\textcolor{r_s}{
		Moschas et al.\cite{Moschas_2014} studied the extraction of strong motion displacement waveform by PPP and evaluated it through free vibration experiments. These results show that 10 Hz PPP-GPS is very useful for seismic engineering and can be safely used to reconstruct the deflection waveforms of various points on the ground and structure during strong motion.}
	\textcolor{r_s}{Zhang et al.\cite{Meng_2019} introduced Galileo augmenting GPS single-frequency single-epoch precise positioning method with baseline constrain for bridge dynamic monitoring, to improve the positioning availability and reliability, as well as narrow the search space, and increase the success rate of ambiguity resolution and positioning.
	Xue et al.\cite{Xue2021} comprehensively evaluated multi-GNSS low-cost receivers for deformation monitoring and concluded that the potential improvement of the precision of the low-cost receiver by using multi-GNSS measurements and a GNSS base station with a geodetic antenna.}
	There are also some studies using the time-differenced carrier phases (TDCP) technique\cite{freda2015time,colosimo2011real} to obtain velocity estimates for displacement detection. This kind of method obtains displacement by integrating velocity, which is mainly used in displacement detection and extraction of large earthquakes.
	In general, the above research mainly focuses on how to improve the positioning accuracy, and the research on how to identify and extract the displacement from the coordinate sequence obtained by GNSS is limited.

	\textcolor{r_s}{
	The other category is displacement detection research based on GNSS.
	There are many studies on the use of high-rate GNSS for structure displacement extraction and parameter identification.
	Psimoulis et al.\cite{psimoulis2008_1,psimoulis2008_2} studied the feasibility of using GNSS for structural vibration detection. Experiments were carried out to evaluate the use of Global positioning system (GPS) to determine the parameters of oscillation of major structures.
	Meng et al.\cite{Meng_2018} presented the challenges faced by the design and implementation of a new monitoring system for large bridges. Damage detection in SHM of long-span bridges is very challenging because there is no general damage definition, and damage is usually unique and bridge-specific. Psimoulis et al.\cite{psimoulis2018detection} presented an algorithm named RT-SHAKE to detect ground motions, which aims to detect seismic motion more sensitively and robustly.	There are also studies on the relationship between receiver parameters and high-rate GNSS measurement\cite{Hberling2015,Moschas2015}.
	H{\"a}berling et al.\cite{Hberling2015} argued that due to the large error of dynamic GNSS measurement if high-rate GNSS is to be a valuable tool for seismic displacement measurement above 1 Hz, the baseband parameters of the GNSS receiver must be considered.
	Moschas et al.\cite{Moschas2015} studied the relationship between the phase-locked loop(PLL) bandwidth and noise in 100 Hz GPS measurement.
	The results show that the measurement correlation decreases with the increase of PLL bandwidth from low to high to 100 Hz. Shen et al.\cite{shennan_2019} gave a more detailed review of dynamic structural health monitoring technology based on GNSS. There are also studies on displacement detection such as landslide, and GNSS is usually used as a static positioning method.}
	Gili et al.\cite{gili2000using} was one of the first landslide monitoring studies using GNSS technology, in which traditional measurement data were used as a comparison. 
	The results showed that the accuracy of the GPS measurement over a period of 26 months was 12 to 16 mm in the horizontal plane and 18 to 24 mm in the elevation.
	A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\cite{rs12203375}. 
	The results of a nine-month of field monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement was obtained by the direct difference between the coordinates of the start and end periods.
	\textcolor{r_s}{
		Betti et al.\cite{betti2001deformation,betti2011deformation} studied the use of the Bayesian approach to evaluating deformation from GPS time series, in which a test procedure was constructed under the Bayesian framework. However, in this method, only specific epochs are tested, and how to identify these epochs is not involved.
		There are also some studies on the significance analysis of the GNSS control network based on the Bayesian test, and the control network processing results are generally based on repeated static adjustment.
	}

@@

	% 仿真实验中不同基于索引检测方法的指标值如图6所示。
	% 从中可以看出不同探测方法所采用的指标的数值范围不一致，但在所设计的突变处很明显。
	%  然而，想基于这些指标值自动将这些突变点识别出来，还需要额外的工作。
	%  另外，这些方法设计之初为了探测突变点，并未涉及位移提取。
	%  有学者，基于设计了基于这些指标的突变探测和位移提取方法，但实时过程复杂。
	%  相比而言，本文提出的方法是一种简单直接易于实现的一站式方法。
	The index values of different index-based detection methods in the simulation experiment are shown in Fig. \ref{fig_v_sim_idx}.
	It can be seen that the numerical range of indicators used by different detection methods is not consistent, but all are obvious at the designed abrupt point.
	However, to automatically identify these abrupt points based on these index values, additional work is required, such as setting a certain threshold.
	In addition, these methods were originally designed to detect abrupt points without involving displacement extraction.
	There are abrupt detection and displacement extraction methods based on these indicators, but the implementation process is complex\cite{shen_shortterm2021}.
	In contrast, the method proposed in this work is a simple, straightforward, and easy-to-implement one-stop method.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_sigma_sim_simple}
		\caption{Histogram of posterior sample of $\sigma$ in the simulation experiment.}
		\label{fig_v_sigma_sim_simple}
	\end{figure} 
	\begin{figure}[htbp]
	\centering
	\includegraphics[scale=0.45]{v_sim_idx}
	\caption{Index values of different index-based detection methods in simulation experiments.}
	\label{fig_v_sim_idx}
	\end{figure} 
	\subsection{Field Experiments}
	The experiments were carried out on the roof of a building on the campus of Wuhan University, and the equipment deployment is shown in Fig. \ref{fig_v_field_exp_config}. 
	A hard plank was pressed with large stones to ensure that the plank remains as fixed as possible during moving the object hanging on the plank. 
	One receiver antenna was fixed on the plank as a rover, and the other receiver antenna was installed on a tripod beside it as the base station. 
	Both antennas were connected to BD992 OEM boards on the table, and the OEM boards were connected to the laptops for data collection. 
	As shown in subgraphs (c) and (d), the height of the antenna was measured with a tape before and after each movement of the object hanging on the plank. 
	\textcolor{r_s}{
		The minimum scale of the tape is 1 mm, that is, the accuracy of the tape is 1 mm, and the estimated reading is 0.1 mm.
		Take five readings for each measurement to ensure the accuracy and reliability of the data.
	}
	Besides, markers are made on the ground and on the antenna respectively to ensure that the same position was referenced for each measurement. 
	The sampling frequency of the GNSS receiver is set to 1 Hz. 
	We did two experiments, each lasting nearly 45 minutes. 
	During the experiment, the object hanging on the board was manually moved several times.
	The displacement amplitude of the second experiment is smaller than that of the first experiment.
	The GNSS observation data collected above are processed by the open-source software RTKLIB\cite{takasu2011rtklib}. 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.5]{v_field_exp_config}
		\caption{Filed experiment configuration. (a) Overview; (b) Working platform; (c) Displacement control platform; (d) Displacement measurement by tape. }
		\label{fig_v_field_exp_config}
	\end{figure}

@@

	For such a short baseline, most of the errors can be eliminated by the double-difference observation. 
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, there are still some unmodeled errors, such as the multipath error that have not been eliminated. 
	The RTK positioning results are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. 
	The histogram of the posterior sample of $\tau$ is shown in Fig. \ref{fig_v_bd9_3_up_tau}.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_tau}
		\caption{Posterior sample distribution of $\tau$ in field experiment 1.}
		\label{fig_v_bd9_3_up_tau}
	\end{figure} 
	From the posterior sample distribution of $\tau_2$ in Fig. \ref{fig_v_bd9_3_up_tau}, one of the change points can be identified as 1897 s. 
	According to the maximum value in the bar chart of the posterior sample of $\tau_1$, the change point is identified as 781 s.
	However, as can be seen from Fig. \ref{fig_v_bd9_3_up_tau}, there are two peaks in the posterior sample distribution of change point $\tau_1$.
	The main reason is that the displacement control device is not completely controllable, and the plank floats up and down when moving the object. 
	In addition, since the antenna is close to the ground, the antenna vibration caused by breeze or touch causes an increase in the multipath phase rate or fading frequency\cite{kelly2003characterization}. 
	The index values of different index-based detection methods in field experiment 1 are shown in Fig. \ref{fig_v_exp1_idx}. At the abrupt point, each index value is no longer as clear as in the simulation experiment, which puts forward higher requirements for additional analysis of these indexes.
	The posterior sample histogram of the $\mu$ of each segment divided by the change point and the displacement measured by the tape are shown in Fig. \ref{fig_v_bd9_3_up_mu} and Table \ref{tab_measured_height_9_3}, respectively.
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_exp1_idx}
		\caption{Index values of different index-based detection methods in field experiment 1.}
		\label{fig_v_exp1_idx}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_mu}
		\caption{Histogram of posterior sample of $\mu$ in field experiment 1.}
		\label{fig_v_bd9_3_up_mu}
	\end{figure} 
	\begin{table}[htbp]
		\centering
		%	\fontsize{6.5}{8}\selectfont
		\begin{threeparttable}
			\caption{Measured height before and after each movement of the object hanging on the plank in field experiment 1, unit (mm).}
			\label{tab_measured_height_9_3}
			\begin{tabular}{ccccccccc}
				\toprule
				&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
				\midrule
				\multirow{3}*{Step 1} 
				& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
				& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
				& & $\Delta h$ & -30.0& -29.8& -29.4& -29.2& -29.9&-29.66\\
				\hline
				\multirow{3}*{Step 2} 
				& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
				& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
				& & $\Delta h$ &-27.5& -27.2& -27.1& -27.0& -27.1& -27.18\\
				\bottomrule
			\end{tabular}
		\end{threeparttable}
	\end{table}

	The $\mu_0$, $\mu_1$, and $\mu_2$ obtained by the mean of the posterior samples are -1446.03 mm, -1474.11 mm, and -1489.83 mm, respectively, and the two displacements obtained by the difference of these mean values are -28.08 mm, -15.72 mm, respectively. The two displacements measured by tape are -29.66 mm and -27.18 mm respectively. 
	To our surprise, the displacement difference between the two methods at the two change points is 1.58 mm and 11.46 mm, respectively. 
	The main reason is that the displacement control device is not fully controllable.
\textcolor{r_s}{
	As can be seen from Fig. \ref{fig_v_bd9_3_up_ts}, the time series fluctuates obviously near the abrupt displacement. To explore the possible causes, the number of satellites, geometric dilution of precision(GDOP), signal-to-noise ratio(SNR), and multipath are shown in Fig. \ref{fig_v_ndop_snrmp_9_3}. The number of satellites and GDOP changed when the displacement took place, which may be caused by the shielding of the antenna during operation. The SNR and multipath have also changed when the displacement takes place, possibly due to antenna vibration caused by touch or wind.}

	As shown in Fig. \ref{fig_v_bd9_3_up_sigma}, the estimated value of $\sigma$ is 12.58 mm through the posterior sample mean of $\sigma$.
	%我们发现此处变点后验样本中的两个峰值对于均值和标准差中没有出现。
	%主要原因是变点的峰值距离很近，对于划分的段没有很明显的影响，因此对后验均值和标准差的浮动没有很大影响。
	%而在现实中，这种情况是会发生的，例如滑坡或者沉降，整个位移变化过程需要一定的时间，存在多个变化点。
	%然而，我们可能更加关注主要变化点，后面通过加入额外先验来提升主要变化点的识别，弱化次要变化点。
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{ndop_snrmp_9_3}
		\caption{Number of satellites, GDOP, SNR, multipath of experiment 1.}
		\label{fig_v_ndop_snrmp_9_3}
	\end{figure} 
	\begin{figure}[htbp]
		\centering
		\includegraphics[scale=0.45]{v_bd9_3_up_sigma}
		\caption{Histogram of posterior sample of $\sigma$ in field experiment 1.}
		\label{fig_v_bd9_3_up_sigma}
	\end{figure} 
	Different from the posterior sample distribution of $\tau$, there is only one peak value in the posterior sample distribution of $\mu$ and $\sigma$.
	The main reason is that the interval of the two peaks is very close, which has little influence on the posterior mean and standard deviation.
	In reality, multiple change points exist, such as multiple displacements in a short period of time in the process of landslide or settlement.
	However, more attention is paid to the primary change points.
	By adding a prior to the model to improve the identification of the primary change points, and weaken the influence of secondary change points will be discussed later.
	\subsubsection{Field Experiment 2}%rover_bd9_4 part(650)
	This experiment is similar to the previous one except that the displacement amplitude is smaller. 
	The coordinate time series is obtained by RTKLIB with the same processing strategy as the previous experiment, and the up component of the time series is shown in Fig. \ref{fig_v_bd9_4_up_ts}. 
	In this experiment, the displacement measured by tape is shown in Table \ref{tab_measured_height_9_4}.

@@

	As can be seen from Fig. \ref{fig_v_bd9_4_up_ts} and Table \ref{tab_measured_height_9_4}, the amplitude of the two displacements is smaller than that of the previous experiment. 
	The time series are processed by the proposed method, and Bayesian inference is implemented by the MCMC sampling. The results are shown in Fig. \ref{fig_v_bd9_4_up_tau}, \ref{fig_v_bd9_4_up_mu}, and \ref{fig_v_bd9_4_up_sigma}.

@@

	The displacement detection based on Bayesian inference can meet different needs by adding a priori, and has sufficient flexibility.
	In addition, the Bayesian inference implementation based on MCMC sampling used in this paper provides posterior samples, which is more conducive to problem analysis.
	This study provides the first comprehensive assessment of the Bayesian inference model for displacement identification and extraction from GNSS kinematic positioning.
	\textcolor{r_s}{
	Although the method is verified with GNSS kinematic data, the method is also suitable for long-term displacement detection. The main difference is the error model and influencing factors considered, which will be carried out in the follow-up work.	
	}
